---
title: "Regression Models Course Project"
author: "Seongsu Kim"
date: "August 18, 2015"
output: pdf_document
---

## Executive Summary
* You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:
    + "Is an automatic or manual transmission better for MPG"
    + "Quantify the MPG difference between automatic and manual transmissions"
    

## Mission
Take the mtcars data set and write up an analysis to answer their question using regression models and exploratory data analyses.

* The report must be:
    + Written as a PDF printout of a compiled (using knitr) R markdown document.
    + Brief. Roughly the equivalent of 2 pages or less for the main text. 
    + Include a first paragraph executive summary.
    

## Exploratory Data Analysis
### 1. To begin with, load the data.

```{r}
data(mtcars)
```

### 2. Here are the details of each column

[, 1]	 mpg	 Miles/(US) gallon

[, 2]	 cyl	 Number of cylinders

[, 3]	 disp	 Displacement (cu.in.)

[, 4]	 hp	 Gross horsepower

[, 5]	 drat	 Rear axle ratio

[, 6]	 wt	 Weight (lb/1000)

[, 7]	 qsec	 1/4 mile time

[, 8]	 vs	 V/S

[, 9]	 am	 Transmission (0 = automatic, 1 = manual)

[,10]	 gear	 Number of forward gears

[,11]	 carb	 Number of carburetors

### 3. By using t-test, we can see the mpg diffence between a manual transmission and an auto transmission.
```{r}
t.test(mpg ~ am, data = mtcars)
```

According to the result shown above,a mean mpg in group 0 which is the group of an automatic transmission is 17.147.
On the other hand, the mean mpg in group 1 which is the group of an manual transmission is 24.39231.
However, we need some more analysis to confirm the result.

```{r, fig.width = 5, fig.height = 4}
mtcars$am[mtcars$am=="0"]<-"Automatic"
mtcars$am[mtcars$am=="1"]<-"Manual"
boxplot(mpg ~ am, data = mtcars, ylab = "mpg", xlab = "Automatic vs. Manual")
```



### 4. Multiple Linear Regression & Residual Plot
```{r}
summary(step(lm(formula = mpg ~ am + qsec+wt, data = mtcars),trace=0,steps=100000))
```
The result above shows that Multiple R-squared is about 85%. It means mpg has 85% of variation.
Also, the coefficient is 2.94. The coefficient in this result means the average of mpg of a manual transmission is 
2.94 higher than the automatic transmission. However, this result doesn't show the relationship with the 
one we got on the second step. The one we got before was 7 which is more than twice bigger than the 2.94.
Also, we can't find heteroskedastic relationship from the residual plot. 
Therefore, I would conclude that it is not possible to determine the better type of transmission for mpg from the data given.  


-----

\newpage


# Appendix


## Residual plot
```{r, fig.width = 3, fig.height = 3,out.extra='angle=90'}
plot(lm(mpg~am + wt + qsec, data = mtcars))
```